Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2022-01-21 ms/data_readme.Rmd
Fix grid-cell descriptions

A list of native, non-hybrid fern specimens housed at the herbarium of the
Museum of Science and Nature, Japan was converted to a community data matrix at
four grain sizes (grid-cells spanning Japan, each 0.1, 0.2, 0.3, or 0.4 degrees
per side). The 0.2 degree grain size was selected for further analysis based on 
redundancy (ratio of number of specimens to number of taxa per cell).

@@

`r fs::path_file(ja_climate_data_file)`: Climate data in Japan downloaded from
WorldClim database (https://worldclim.org/data/v1.4/formats.html). Raw data were
downloaded at the 2.5 minute scale. The intersection of the raw climate data
with 0.2 degree grid-cells (japan_ferns_shape_full.gpkg) were identified,
then average value for each climatic variable was calculated for each grid-cell.

@@

`r fs::path_file(japan_ferns_comm_full_file)`: Community matrix (species x sites
matrix) of native, non-hybrid ferns in Japan. Sites correspond to 0.2 degree x
0.2 degree grid-cells covering Japan. For location of grid-cells, see
japan_ferns_shape_full.gpkg. Full dataset including all grid-cells (none
excluded due to low redundancy).

@@

```{r redundancy-by-res-cols, results = "asis"}
  redundancy_by_res %>%
  make_data_desc(
    tribble(
      ~col, ~desc,
      "res", "Degree of resolution (grid-cell side length), from 0.1 to 0.4 degrees",
      "grids", "Name of grid-cell",
      "richness", "Number of taxa occurring in grid-cell",
      "abundance", "Number of specimens occurring in grid-cell",
      "redundancy", "Redundancy (measure of sampling completeness)"
  ))
```

@@

`r fs::path_file(japan_ferns_shape_full_file)`: Location of grid-cells (sites)
for native, non-hybrid ferns in Japan in GeoPackage format. Compiled from raw
specimen data by binning specimens into 0.2 degree grid-cells across Japan. Full
dataset including all grid-cells (none excluded due to low redundancy).

@@

>>>>

A list of native, non-hybrid fern specimens housed at the herbarium of the
Museum of Science and Nature, Japan was converted to a community data matrix at
four grain sizes (square grid-cells spanning Japan, each 10, 20, 30, or 40 km
per side). The 20 km degree grain size was selected for further analysis based 
on redundancy (ratio of number of specimens to number of taxa per cell).

@@

`r fs::path_file(ja_climate_data_file)`: Climate data in Japan downloaded from
WorldClim database (https://worldclim.org/data/v1.4/formats.html). Raw data were
downloaded at the 2.5 minute scale. The intersection of the raw climate data
with 20 km × 20 km grid-cells (japan_ferns_shape_full.gpkg) were identified,
then average value for each climatic variable was calculated for each grid-cell.

@@

`r fs::path_file(japan_ferns_comm_full_file)`: Community matrix (species x sites
matrix) of native, non-hybrid ferns in Japan. Sites correspond to 20 km x
20 km grid-cells covering Japan. For location of grid-cells, see
japan_ferns_shape_full.gpkg. Full dataset including all grid-cells (none
excluded due to low redundancy).

@@

```{r redundancy-by-res-cols, results = "asis"}
  redundancy_by_res %>%
  make_data_desc(
    tribble(
      ~col, ~desc,
      "res", "Degree of resolution (grid-cell side length), from 10 to 40 km (in m)",
      "grids", "Name of grid-cell",
      "richness", "Number of taxa occurring in grid-cell",
      "abundance", "Number of specimens occurring in grid-cell",
      "redundancy", "Redundancy (measure of sampling completeness)"
  ))
```

@@

`r fs::path_file(japan_ferns_shape_full_file)`: Location of grid-cells (sites)
for native, non-hybrid ferns in Japan in GeoPackage format. Compiled from raw
specimen data by binning specimens into 20 km × 20 km grid-cells across Japan. 
Full dataset including all grid-cells (none excluded due to low redundancy).

@@

Coordinate reference system: Mollweide (+proj=moll +lon_0=135)
